\documentclass{article}

\usepackage{fontawesome}
\usepackage[margin=1.8cm]{geometry}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\pagestyle{empty}
\raggedright

\newcommand{\contact}[2]{
    \begin{center}
    {\LARGE \uppercase {#1}} \\
    \vspace{8pt}
    #2
    \end{center}
}

\newcommand{\header}[1]{
    {
        \hspace*{-4pt}
        \vspace*{8pt}
        \uppercase{#1}
    }
    \vspace*{-4pt} 
    \lineunder
    \vspace*{8pt}
}

\newcommand{\lineunder}{
    \vspace*{-8pt} \\ 
    \hspace*{-4pt} 
    \hrulefill \\
}

\newcommand{\experience}[5]{
    \vspace*{2pt}
    \textbf{#1}, #2 \hfill #3 \\ 
    #4 \\
    #5
    \vspace*{2pt}
}

\newcommand{\bigdot}{
    $\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{2pt}
}

\newcommand{\spacedbullet}{
    $\vcenter{\hbox{\tiny$\bullet$}}$\hspace*{-2pt}
}

\newenvironment{bulletlist}{
    \begin{list}
        {\spacedbullet}{\setlength\leftmargin{10pt} 
        \topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\begin{document}
\small

\vspace*{-32pt}

\contact{Niels Degrande}
{
    \faPhone\ \href{tel:+46722156403}{+46 72-215 6403}
    \bigdot \faEnvelope\ \href{mailto:niels@degran.de}{niels@degran.de}
    \bigdot \faGlobe\ \href{https://niels.degran.de}{niels.degran.de}
    \bigdot \faGithub\ \href{https://github.com/NielsDegrande}{NielsDegrande}
    \bigdot \faLinkedin\ \href{https://linkedin.com/in/nielsdegrande}{nielsdegrande}
}

\vspace{16pt}

\header{Professional Summary}
\begin{bulletlist}
    \item Lead multi-team AI engineering efforts across 20+ deployments, delivering measurable impact.
    \item Build, deploy, and scale GenAI, ML, and optimization solutions from concept to production using modern MLOps practices.
    \item Drive org-wide adoption through hands-on development, platform engineering, and cross-functional technical leadership.
\end{bulletlist}

\vspace*{4pt}

\header{Work Experience}
\experience{AI Research Engineer (Technical Staff)}{Lovable}{2026 -- Present}{Stockholm, Sweden}
{
    \begin{bulletlist}
        \item Make Lovable more lovable.
    \end{bulletlist}
}

\experience{Partner AI Engineer}{Boston Consulting Group X \textit{— BCG's tech build and design unit}}{2024 -- 2026}{Stockholm, Sweden}
{
    \begin{bulletlist}
        \item Designed and built a greenfield data and (Gen)AI platform for connected appliances, enabling 10--100$\times$ scaling while controlling costs and reducing time-to-deploy from months to weeks.
        \item Built GenAI and ML solutions to reformulate products and automate regulatory document writing.
        \item Improved marketing workflows with constrained agents and RAG, achieving up to 65\% time savings at the same or better quality while reducing agency costs.
    \end{bulletlist}
}

\experience{Principal AI Engineer}{Boston Consulting Group X}{2022 -- 2024}{Stockholm, Sweden}
{
    \begin{bulletlist}
        \item Built an LLM-based web app to automate annual report analysis and drafting (multi-query, rerank, evaluations, LLMOps).
        \item Developed GenAI products (OpenAI, LangChain, Langfuse) for field support, personalization, and supply chain simulations.
        \item Led hands-on GenAI workshops for executives and developer teams.
        \item Predicted logistics demand (LightGBM) and optimized shipping routes (constraint programming) to reduce vessels.
        \item Conducted technology stack due diligence and code review for a software company considered for acquisition.
        \item Established data platforms (ADF, Databricks, dbt, Airflow) for an automotive supplier and for company-wide use, supporting 10+ AI products and BI reports.
        \item Scaled model executions on ACI with Airflow orchestration and AzureML tracking, exposed via an API.
    \end{bulletlist}
}

\experience{Lead AI Engineer}{Boston Consulting Group GAMMA \textit{— BCG's data science unit}}{2020 -- 2022}{Stockholm, Sweden}
{
    \begin{bulletlist}
        \item Forecasted timber demand (using several learners), with model lifecycle managed via MLflow \& AzureML.
        \item Built React + TypeScript web application to interface with optimization and simulation models.
        \item Led development \& scaling of supply chain solutions (OR-Tools, Gurobi) contributing to 4-6\% EBITDA uplift.
        \item Built and deployed an ML-based pricing algorithm with AKS, AzureML, Elasticsearch, and LightGBM.
        \item Trained teams on Dev/MLOps: infra-as-code, CI/CD, feature stores, model management, monitoring, etc.
    \end{bulletlist}
}

\experience{Senior AI Software Engineer}{Boston Consulting Group GAMMA}{2016 -- 2020}{Brussels, Belgium $\rightarrow$ Stockholm, Sweden}
{
    \begin{bulletlist}
        \item Deployed Bayesian inference investment algorithm worldwide (PyStan, Alibaba Cloud, GCP, Terraform).
        \item Developed multi-echelon optimization model for postal services to enhance delivery efficiency.
        \item Hardened and industrialized ML and optimization using AKS, C\#, Jenkins, and Helm to quantify assortments.
        \item Built cloud-based big data platform with Airflow, Ansible, Hive and Spark.
    \end{bulletlist}
}

\vspace*{4pt}

\header{Education}
\experience{Bachelor and Master of Science: Information Systems Engineering}{KU Leuven}{2011 -- 2016}{Leuven, Belgium}
{
    \begin{bulletlist}
        \item Specialization: Computer Architecture, Internet Infrastructure, and Big Data.
        \item Graduated Summa Cum Laude with Congratulations of the Board of Examiners.
        \item Exchange Programs: University of Pennsylvania (2013) and Peking University (2015).
    \end{bulletlist}
}

\vspace*{4pt}
\header{Skills \& Projects}
\begin{bulletlist}
    \item Refer to my \href{https://linkedin.com/in/nielsdegrande/}{LinkedIn profile} for a detailed list of technical skills, certifications, publications, languages, and awards.
    \item Visit my \href{https://github.com/NielsDegrande/}{GitHub} and \href{https://niels.degran.de/blog}{personal blog} for an overview of projects and writings.
\end{bulletlist}

\end{document}
